Ms 1

### 2017-08-23 ms1/ms1_display.Rmd
RR, broke up table

### Unadjusted trends

@@

Second, I do logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The odds ratio is between 2011 and 2014. (I'll convert that into a risk ratio using the 2011 probabilities.)

@@

 bind_rows(dx_pde_unadj, dx_pde_adj) %>%
   spread(key, value) %>%
   mutate(pct_change=(y2014/y2011-1)*100,
          adj_pct_change=(rr(OR, y2011)-1)*100) %>%
   select(-OR) %>%
   #mutate_if(is.numeric, function(x) round(x, 2)) %>%
   gather('key', 'value', y2011:adj_pct_change) %>%
   mutate(value=round(value, 2)) %>%
   spread(diagnosis_category, value) %>%
   mutate(key=factor(key, levels=c('y2011', 'y2014', 'pct_change', 'adj_pct_change'))) %>%
   arrange(antibiotic, key) %>%
   kable
```

>>>>

@@

Second, I do logistic regressions. The unit of analysis is the diagnosis. The outcome is whether a PDE for that drug follows a diagnosis in that category. The main predictor is year; covariates are as above. The adjusted percent change is between 2011 and 2014. (I computed this adjusted change, which is a relative risk, using the odds ratio from the regression and the mean probability of PDE for that diagnosis in 2011. This strictly incorrect: the mean relative risk is the mean of the risks computed using the predicted probabilities for each 2011 diagnosis, *not* the relative risk computed using the mean probability in 2011. But it seems like it's decently close, and I think insisting on the thing that is technically correct will only create confusion.)

I broke this into three tables by antibiotic, just to make it easier to navigate.

@@

dx_pde_both= bind_rows(dx_pde_unadj, dx_pde_adj) %>%
   spread(key, value) %>%
   mutate(pct_change=(y2014/y2011-1)*100,
          adj_pct_change=(rr(OR, y2011)-1)*100) %>%
   select(-OR) %>%
   #mutate_if(is.numeric, function(x) round(x, 2)) %>%
   gather('key', 'value', y2011:adj_pct_change) %>%
   mutate(value=round(value, 2)) %>%
   spread(diagnosis_category, value) %>%
   mutate(key=factor(key, levels=c('y2011', 'y2014', 'pct_change', 'adj_pct_change'))) %>%
   arrange(antibiotic, key)

dx_pde_both %>%
  filter(str_detect(antibiotic, '^a')) %>%
   kable

dx_pde_both %>%
  filter(str_detect(antibiotic, '^c')) %>%
   kable

dx_pde_both %>%
  filter(str_detect(antibiotic, '^[^ac]')) %>%
   kable
```
